Beyond body length: Uncovering the drivers of vertebra number variation in Australian blindsnakes

### 2025-04-10 manuscript.Rmd
update latest manuscript before acceptance

<!-- Fig: Pleomerism and ratio correlations -->
```{r fig-vert-aspect-ratios, fig.cap =  'Species mean aspect ratios against (A) mean vertebra ratio and (B) mean number of vertebrae of Australian blindsnakes. Vertebra ratio is calculated by total vertebrae/TBL, and aspect ratio is TBL/MBD. Inset images of vertebral profile shape in (A) represent different vertebra ratios, and are depicted as a 4° polynomial curve with positive inflection. Species with large aspect ratios are narrow-and-long while species with low aspect ratios robust-and-wide. Phylogeny projected into space using maximum likelihood ancestral state estimation. Species not included in the phylogeny are shown in purple.', out.width = "124mm", out.height =  "165mm"}

@@

<!-- Fig: Ratio and ecological variables -->
```{r fig-vert-ecology, fig.cap= 'Phylomorphospaces showing relationship between mean vertebra ratios and mean number of vertebrae against ecological variables. Mean vertebra ratio against (A) species mean annual temperature and (B) species max soil bulk density. Mean vertebra ratio is calculated by mean total vertebrae / mean TBL for each species. Mean number of vertebrae against (C) species mean annual temperature and (D) species max soil bulk density. Species mean annual temperature and max soil bulk density values are calculated based on occurrence data. Trend lines represent slopes from PGLS', out.width="165mm", out.height= "117mm"}

>>>>

<!-- Fig: Pleomerism and ratio correlations -->
```{r fig-vert-aspect-ratios, fig.cap =  'Species mean aspect ratios against (A) mean vertebra ratio and (B) mean number of vertebrae of Australian blindsnakes. Vertebra ratio is calculated by total vertebrae/TBL, and aspect ratio is TBL/MBD. Inset images of vertebral profile shape in (A) represent different vertebra ratios, and are depicted as a 4° polynomial curve with positive inflection. Species with large aspect ratios are narrow-and-long while species with low aspect ratios robust-and-wide. Phylogeny projected into space using maximum likelihood ancestral state estimation. Species not included in the phylogeny are shown in purple.', out.width = "152mm", out.height =  "196mm"}

@@

<!-- Fig: Ratio and ecological variables -->
```{r fig-vert-ecology, fig.cap= 'Phylomorphospaces showing relationship between mean vertebra ratios and mean number of vertebrae against ecological variables. Mean vertebra ratio against (A) species mean annual temperature and (B) species max soil bulk density. Mean vertebra ratio is calculated by mean total vertebrae / mean TBL for each species. Mean number of vertebrae against (C) species mean annual temperature and (D) species max soil bulk density. Species mean annual temperature and max soil bulk density values are calculated based on occurrence data. Dashed trend lines represent slopes from PGLS', out.width="165mm", out.height= "117mm"}
